\documentclass[10pt, hidelinks]{article}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{array}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=10mm,
 right=20mm,
 top=10mm,
 }
\begin{document}
	% Personal Information

	\begin{minipage}[t]{0.46\textwidth}
		{\Huge\color{RoyalBlue}Tarun Kumar}\\
		{\Large\textbf{I}nstitute of \textbf{E}ngineering \textbf{T}echnology \textbf{L}ucknow}
	\end{minipage}
	\begin{minipage}[t]{0.54\textwidth}
		\begin{flushright}
			{\small
			Third Year \textbf{Undergraduate}, {\color{RoyalBlue}Information Technology\\}
			{\color{RoyalBlue}Add: }{H-124 Jankipuram Garden, Lucknow, Uttar Pradesh\\}
			{\color{RoyalBlue}E-Mail: }{\href{mailto:tarunkumar281200@gmail.com}{tarunkumar281200@gmail.com}\\}
			{\color{RoyalBlue}Mobile: }{+91 9628907499\\}
			{\color{RoyalBlue}LinkedIn: }{\href{https://www.linkedin.com/in/tarun-kumar-7489651a0/}{tarun-kumar}\\}
			{\color{RoyalBlue}GitHub: }{\href{https://github.com/Tarun-19}{Tarun-19}\\}
			}
		\end{flushright}
	\end{minipage}

	% Education Information

	{\large\color{RoyalBlue}Education}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}
	\begin{center}
		{\small \vspace*{-5mm}
		\begin{tabular}{ m{0.6\textwidth} m{0.15\textwidth} m{0.15\textwidth}}
			BTech, Information Technology:\\ Institute of Engineering Technology, Lucknow & CGPA: 8.04/10 & 2019 - PRESENT \\
			Class 12: Lucknow Public College & Aggregate: 89\% & 2014-2018 \\
		\end{tabular}
		}
	\end{center}

	% Experiences/Internships

	{\large\color{RoyalBlue}Experience}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}

	{\vspace*{-3mm}\normalsize\textbf{Interned at ABC under Mr. XYZ}} {\small[\href{https://httpbin.com}{Offer Letter/LinkedIn Post/Report}]} \hspace*{8pt} {\normalsize\textit{(202X-202X)}}
	{\vspace*{-3mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Worked on this thing for this much amount of time.
		\item Gained Industry level knowledge about this field
		\item Gained experience in this, that and these tools.
	\end{itemize}
	}
	{\vspace*{-3mm}\normalsize\textbf{Interned at ABC under Mr. XYZ}} {\small[\href{https://httpbin.com}{Offer Letter/LinkedIn Post/Report}]} \hspace*{8pt} {\normalsize\textit{(20XX-20XX)}}
	{\vspace*{-3mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Worked on this thing for this much amount of time.
		\item Gained Industry level knowledge about this field
		\item Gained experience in this, that and these tools.
	\end{itemize}
	}

	% Projects

	{\large\color{RoyalBlue}Projects}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}

	{\vspace*{-3mm}\normalsize\textbf{Designed an Object-oriented design of digital filtering in scipy.signal}} {\small[\href{https://httpbin.com}{Offer Letter/LinkedIn Post/Report}]} \hspace*{8pt} {\normalsize\textit{(20XX-20XX)}}
	{\vspace*{-3mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Worked on this thing for this much amount of time.
		\item Worked with Python, API design. Gained experience in Digital Signal Processing.
	\end{itemize}
	}
	{\vspace*{-3mm}\normalsize\textbf{Created a time machine from a microwave oven and a Motorola switch phone}} {\small[\href{https://httpbin.com}{Offer Letter/LinkedIn Post/Report}]} \hspace*{8pt} {\normalsize\textit{(20XX-20XX)}}
	{\vspace*{-3mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Worked creating a D-Mail machine to send message to the past for three weeks.
		\item Gained Industry level knowledge Microwave ovens, Motorola Switch Phones and Kerr Black Holes.
	\end{itemize}
	}

	% Skills section

	{\large\color{RoyalBlue}Skills}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}
	\begin{center}
		{\vspace*{-3mm}\small \vspace*{-5mm}
		\begin{tabular}{ m{0.3\textwidth} m{0.7\textwidth}}
			\textbf{Languages known} & :Python, NodeJS, Java, SQL, VHDL, RISC-V Assembly(Basic), C++(Familiar) \\
			\textbf{Familiar Libraries/Framworks} & :Express, Flask, Pandas, Numpy, Pytest, Jest, Scipy, Matplotlib \\
			\textbf{Concepts Experienced in} & :Backend development, Testing, CI/CD, Machine Learning, Cloud Native Development, Cloud Services \\
			\textbf{Database} & :MongoDB, Posgresql, MariaDB \\
			\textbf{Relevant Coursework} & :Digital Electronics, Computer Architecture, Data Structures and Algorithms, Electronic Devices, Machines \\
		\end{tabular}
		}
	\end{center}

	% Positions of responsibility

	{\large\color{RoyalBlue}Positions of Responsibility}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}
	\begin{center}
		{\vspace*{-3mm}\small \vspace*{-5mm}
		\begin{tabular}{ m{0.3\textwidth} m{0.5\textwidth} m{0.2\textwidth}}
			\textbf{Music Club Head} & :Position under General Secretary of IIT Goa, leading, managing and organising activites of the Music Club, Orion & (2020-2021) \\
			\textbf{Coordinator at Cultural Fest} & :Planned, managed and coordinated various events and competitions at Cultural Fest of IIT Goa & (May 2021) \\
			\textbf{Backend Developer} & :Created the backend of the website for Cultural fest of IIT Goa & (May 2021) \\
			\textbf{Internship Coordincator} & :Coordinator of Internships for Electrical Engineering Department & (2021-2022) \\
			\textbf{Maintainer} & :Mainainer of an Open Soure Project, Dynamic CLI, Indian Open Source Foundation & (2021-Present) \\
		\end{tabular}
		}
	\end{center}

	% Achievements

	{\large\color{RoyalBlue}Achievements}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}
	\vspace*{-10mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Successfully defeated Thanos by acquiring all the infinity stones
		\item Made a Fully Autonomous ballastic suit from scraps in a cave file held captives by Al Qaida.
		\item Genius, Billionaire, Playboy, Philanthrophist
	\end{itemize}

	{\large\color{RoyalBlue}Extracurriculars and Hobbies}
	\par\noindent\rule[7pt]{\textwidth}{0.1pt}
	\vspace*{-10mm}
	\begin{itemize}
		\itemsep-0.3em
		\item Organised and participated in several events in college (Cultural Fests, Technical events, Independence Day, Republic Day etc)
		\item Playing keyboard and music mixing.
		\item Playing online games and watching anime.
	\end{itemize}

\end{document}
